### 2016-12-29 paper/paper.tex
abstract

\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\Gaia}{\project{Gaia}}

@@

\section*{\raggedright%
A photometric method for obtaining spectroscopic parameters of stars}

@@

\paragraph{Abstract:}
foo and bar

>>>>

\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\Gaia}{\project{Gaia}}
\newcommand{\GALEX}{\project{\acronym{GALEX}}}
\newcommand{\APASS}{\project{\acronym{APASS}}}
\newcommand{\RAVEon}{\project{\acronym{RAVE}-on}}

@@

\section*{\raggedright%
A photometric method for obtaining spectroscopic parameters of stars,
with no use of physical models}

@@

\paragraph{Abstract:}
% Context
Stellar photospheres, to first order, have their spectral properties
set by the local quantities (spectroscopic parameters) effective
temperature, surface gravity, and metallicity (chemical composition);
As their name suggests, spectroscopic parameters can be determined
with stellar spectra and photosphere models.
Global stellar structure, including radii, masses, and bolometric
luminosities cannot be predicted theoretically without a physical
model of stellar structure or stellar evolution.
The \Gaia\ Mission has already delivered parallaxes---and therefore
luminosity information---for millions of stars; \GALEX\ and
\APASS\ deliver multi-band photometry; for a subset, \RAVEon\ delivers
spectroscopic parameters.
% Aims
In this project, we infer spectroscopic parameters for stars for which
only photometry and astrometry is available.
We make no use of stellar structure or evolution models.
% Methods
After showing empirically that stars with similar luminosities and
colors have similar spectroscopic parameters, we train a very flexible
regression model of the relationship between luminosity, color, and
the spectroscopic parameters.
The model is a modification of a k-nearest-neighbors method.
We use this model to paint spectroscopic parameters onto stars that have
not been observed spectroscopically.
% Results
We find XXX and YYY. Things degrade in ZZZ way when WWW.
